---
title: "Oncology - Q1 Journal list"
date: '2022-04-12T22:13:27+03:00'
subtitle: 'List of all Q1 Journals (WOS-IF) in the category "Oncology"'
summary: 'List of all Q1 Journals (WOS-IF) in the category "Oncology"'
authors: [admin]
slug: oncology-q1-2022
categories:
  - AcadeMD
tags:
  - WOS
lastmod: '2022-04-12T16:13:27+03:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: 
  - AcadeMD
links:
 - icon: github
   icon_pack: fab
   name: GitHub
   url: "https://github.com/AliGunerMD/aliguner/blob/main/content/post/2022-04-12-oncology-q1-2022/index.en.Rmd"
 - icon: link
   icon_pack: fas
   name: Clarivate
   url: "https://jcr.clarivate.com/jcr/browse-journals"
url_pdf: ""
url_code: ""
url_dataset: ""
url_project: ""
url_slides: ""
url_source: ""
url_video: ""
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```


```{r import library}
library(tidyverse)
library(scales)
library(readxl)
library(here)
library(janitor)
library(flextable)
library(ggrepel)
theme_set(theme_light())

myblues <- c("#F7FBFF", "#DEEBF7", "#C6DBEF", "#9ECAE1", "#6BAED6", "#4292C6", "#2171B5" ,"#084594")
```



```{r}
imported_data <- read_csv(here("datasets", "wos_2022_oncology.csv"),
         skip = 2,
         na = c("n/a", "N/A", "")) %>% 
  clean_names() %>% 
  slice(1:(nrow(.)-2)) 

```


Here is the example of WOS dataset downloaded from the [Journal Citation Reports](https://jcr.clarivate.com/jcr/browse-journals). Filters were;   
**Categories:** Oncology  
**JCR Year:** 2020  (Up-to-date list)  
**Citation indexes:** SCIE, ESCI  

Original dataset includes `r nrow(imported_data)` rows and `r ncol(imported_data)` columns. Only `r imported_data %>% count(category) %>% filter(category == "ONCOLOGY - SCIE") %>% pull(n)` are indexed in SCIE, and remaining `r imported_data %>% count(category) %>% filter(category == "ONCOLOGY - ESCI") %>% pull(n)` journals are in ESCI index.

# Original dataset
```{r}
set.seed(2020)
imported_data %>% 
  sample_n(6) %>% 
  knitr::kable(caption = "An example of WOS dataset (6 random rows)")
```

<br>

# Full list 

```{r}
clean_data <- imported_data %>% 
  mutate(across(everything(), ~str_replace_all(., ",", ""))) %>% 
  mutate(journal_name = str_to_title(journal_name),
         journal_name = if_else(str_detect(journal_name, "Jama"), str_replace_all(journal_name, "Jama", "JAMA"), journal_name),
         journal_name = if_else(str_detect(journal_name, "Ejso"), str_replace_all(journal_name, "Ejso", "EJSO"), journal_name),
         journal_name = if_else(str_detect(journal_name, "Esmo"), str_replace_all(journal_name, "Esmo", "ESMO"), journal_name),
         journal_name = if_else(str_detect(journal_name, "Jnci-"), str_replace_all(journal_name, "Jnci-", "JNCI-"), journal_name),
         journal_name = if_else(str_detect(journal_name, "Npj "), str_replace_all(journal_name, "Npj ", "npj "), journal_name), 
         journal_name = if_else(str_detect(journal_name, " Of "), str_replace_all(journal_name, " Of ", " of "), journal_name),
         journal_name = if_else(str_detect(journal_name, " Et "), str_replace_all(journal_name, " Et ", " et "), journal_name),
         journal_name = if_else(str_detect(journal_name, " And "), str_replace_all(journal_name, " And ", " and "), journal_name),
         journal_name = if_else(str_detect(journal_name, " The "), str_replace_all(journal_name, " The ", " the "), journal_name),
         journal_name = if_else(str_detect(journal_name, " In "), str_replace_all(journal_name, " In ", " in "), journal_name),
         journal_name = if_else(str_detect(journal_name, " For "), str_replace_all(journal_name, " For ", " for "), journal_name)) %>% 
      mutate(across(everything(), ~str_replace_all(., ",", " "))) %>% 
  mutate_at(c("total_citations", "x2020_jif", "x2020_jci", "x5_year_jif", "jif_without_self_cites", "immediacy_index", "normalized_eigenfactor", "eigenfactor", "article_influence_score", "jif_percentile", "total_articles", "citable_items"), as.numeric)
```


```{r}
link <- "https://jcr.clarivate.com/jcr/browse-journals"




table_2022_q1 <- clean_data %>% 
  filter(jif_quartile == "Q1") %>% 
  select(journal_name, x2020_jif, jif_without_self_cites,  total_citations, total_articles, citable_items)
```


```{r}
table_q1_2022_oncology <- table_2022_q1 %>% 
  flextable() %>%
  set_table_properties(width = 1, layout = "autofit") %>% 
  set_header_labels(i = 1, "journal_name" = "Journal name", "x2020_jif" = "Impact factor",  "jif_without_self_cites" = "IF without self-citation" , "total_citations" = "# of citations", "total_articles" =  "# of articles", "citable_items" = "# of citable items" ) %>% 
 theme_booktabs() %>% 
 align(part = "all", align = "center", j=2:ncol(table_2022_q1)) %>% 
 add_header_lines(paste0('The list of ',nrow(table_2022_q1),' WOS-Q1 journals in the category "Oncology" \n(year = 2020, released in 2021)')) %>% 
 fontsize(part = "header", size = 14, i = 1) %>% 
 align(part = "header", align = "center", i=1) %>% 
 align(part = "header", align = "center", i=2, j = 2:ncol(table_2022_q1)) %>% 
 bold(part = "header") %>% 
 color(part = "header", i=1, color = "#666666") %>% 
 bg(bg = myblues[4], part = "header", i=2) %>% 
 border_remove(.) %>% 
 hline(part="header", i = 1:2) %>% 
 hline(part="body", i = nrow(table_2022_q1)) %>% 
 add_footer_lines ("Source: Clarivate") %>% 
 color(part = "footer", color = "#666666") %>% 
 align(part = "footer", align = "right",  i=1) %>% 
 compose(part = "footer", value = as_paragraph(hyperlink_text(x= "Data source: Clarivate", url = link))) %>% 
 add_footer_lines("designed by @AliGunerMD")
```

```{r}
table_q1_2022_oncology
```


```{r}
# Featured figure
 
 labelInfo <- data.frame(
  g = c("Ca-A Cancer Journal for Clinicians (IF = 508.7) and \n
    Cancers (citable items = 3740) were ignored "))
  
 
 set.seed(2022)
 figure_q1_onc <- table_2022_q1 %>% 
  arrange(desc(x2020_jif)) %>% 
  filter(!journal_name %in% c("Ca-A Cancer Journal for Clinicians", "Cancers")) %>% 
  ggplot(aes(citable_items, x2020_jif, label = journal_name)) +
  geom_point(aes(color = x2020_jif, size = total_citations)) +
  scale_color_continuous(type = "viridis", trans = 'reverse') +
  scale_y_continuous(labels = number_format(accuracy = 1), breaks = seq(0, 70, 10), expand = c(0, 0), limits = c(0, 70)) +
  scale_x_continuous(labels = comma_format(), breaks = c(0,100,200, 300, 400, 500, 1000), expand = c(0, 0), limits = c(0, 1000)) +
  scale_size(breaks = c(1e4, 2.5e4, 5e4, 10e4, 15e4,  20e4), labels = c("10k", "25k", "50k","100k","150k","200k")) +
  expand_limits(y = 0) +
  labs(title = 'WOS-Q1 journals in the category "Oncology" ',
       subtitle = "Relationship among the IF, the # of citable items, and the # of total citations",
       y = "Impact factor",
       x = "Citable items",
       size = "# of citations",
       caption = "Data source: Clarivate\ndesigned by @AliGunerMD") +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_line(color = "#E8E8E8"),
        plot.title = element_text(hjust = .5, face = "bold"),
        plot.subtitle = element_text(hjust = .5),
        panel.border = element_blank(),
        axis.line =  element_line(color = "#404040"),
        axis.ticks = element_line(color = "#101010")) +
  guides(color = "none", 
         size = guide_legend(reverse = TRUE,
                         title.hjust = 0.5,
                         label.hjust = 1)) +
   geom_text_repel(
     data = subset(table_2022_q1, x2020_jif > 60),
     nudge_x = 200,
     box.padding = 0.5,
     nudge_y = 0,
     segment.size  = 0.2,
     segment.color = "#C0C0C0",
     direction = "x",
     max.iter = Inf) +
   geom_text_repel(
     data = subset(table_2022_q1, x2020_jif > 20 &  x2020_jif < 60),
     nudge_x = 200,
     box.padding = 0.5,
     nudge_y = 5,
     segment.size  = 0.2,
     segment.color = "#C0C0C0",
     direction = "x",
     max.iter = Inf) +
    geom_text_repel(
     data = subset(table_2022_q1, x2020_jif < 20 & x2020_jif > 13 &  citable_items < 200),
     nudge_x = 20,
     box.padding = 0.5,
     nudge_y = 10,
     segment.size  = 0.2,
     segment.color = "#C0C0C0",
     direction = "y") +
   geom_text_repel(
     data = subset(table_2022_q1, citable_items > 400),
     nudge_x = 100,
     box.padding = 0.5,
     nudge_y = 12,
     segment.size  = 0.2,
     segment.color = "#C0C0C0",
     direction = "y",
     max.iter = Inf) +
   geom_label_repel(
     data = labelInfo, 
     mapping = aes(800, 65, label = g),
     size = 4,
     hjust = c(0))
 
 ggsave(
   figure_q1_onc,
   file =file.path ("featured.jpg"), 
   width = 9.7,
   height = 8.1
   )
 
 

```


